LAGOS lake depth

### 2020-12-07 figures/01_geometry.Rmd
add axis superlabels

cowplot::plot_grid(
  gg_dist_base, 
  gg_slope_base, 
  rel_widths = c(1, 0.9)
)

>>>>

cowplot::plot_grid(
  ggdraw() + 
    draw_label("True measures", y = 0.37, hjust = 0, size = 12, angle = 90,  fontface = "bold"), 
cowplot::plot_grid(
  cowplot::plot_grid(
    gg_dist_base, 
    gg_slope_base, 
    rel_widths = c(1, 0.9)
  ), 
  ggdraw() + 
    draw_label("Proxy measures", x = 0.45, hjust = 0, size = 12, fontface = "bold"),
  ncol = 1, rel_heights = c(1, 0.1)),
ncol = 2, rel_widths = c(0.1, 1))
